Making Sequential Programs Deterministic

### 2019-04-06 design.tex
Fix LaTeX error

More specifically, rule \rulename{set precision} of
\cref{fig-precision-rules} expresses that the return type of \<equals()>
is \<Det> if both arguments have type \<OrderNonDet Set> and neither argument
has \code{@OrderNonDet List} or a subtype within its type argument.
Without this rule, the type would be \<NonDet> which is sound but imprecise.

>>>>

More specifically, rule \rulename{set precision} of
\cref{fig-precision-rules} expresses that the return type of \<equals()>
is \<Det> if both arguments have type \<OrderNonDet Set> and neither argument
has \codeid{@OrderNonDet List} or a subtype within its type argument.
Without this rule, the type would be \<NonDet> which is sound but imprecise.
